Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools

### 2024-03-27 paper.tex
Fix up table 1 location
Add v2 sub files

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools},
  pdfauthor={Robin Lovelace; Joey Talbot; Eugeni Vidal-Tortosa; Hussein Mahfouz; Elaine Brick; Peter Wright; Gary O'Toole; Dan Brennan; Suzanne Meade},
  pdfkeywords={Cycling, Open-source, Road Safety, Active
Travel, Transport Planning, Collaborative Planning},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Cycle Route Uptake and Scenario Estimation (CRUSE): an approach
for developing strategic cycle network planning tools}
\author[1]{Robin Lovelace%
\corref{cor1}%
}
 \ead{r.lovelace@leeds.ac.uk} 
\author[1]{Joey Talbot%
%
}

\author[1]{Eugeni Vidal-Tortosa%
%
}

\author[1]{Hussein Mahfouz%
%
}

\author[2]{Elaine Brick%
%
}

\author[3]{Peter Wright%
%
}

\author[2]{Gary O'Toole%
%
}

\author[4]{Dan Brennan%
%
}

\author[4]{Suzanne Meade%
%
}

\affiliation[1]{organization={University of
Leeds},addressline={Institute for Transport Studies, Leeds, LS2 9JT,
United Kingdom},postcodesep={}}
\affiliation[2]{organization={AECOM},addressline={Unit 6, Galway
Technology Park, Parkmore, Galway, Ireland},postcodesep={}}
\affiliation[3]{organization={AECOM},addressline={Winslade House,
Winslade Park, Manor Drive, Clyst St Mary, Exeter, EX5 1FY,
UK},postcodesep={}}
\affiliation[4]{organization={Transport Infrastructure
Ireland},addressline={Parkgate Business Centre, Parkgate Street, Dublin
8, D08 DK10, Ireland},postcodesep={}}

@@

Previous studies have applied the concept of PSS to specific modes,
including walking \citep{bencekri2024}, public transport
\citep{barmentlo2012} and cycling \citep{bencekri2023}. While such prior
work provides insight into the potential for approaches to transport
planning that are both data-driven and participatory, the focus of this
paper is on tools that focus attention on the \emph{geographic
distribution} of cycling potential and which answer the question ``where
to build''. Not all papers reviewed in this section classify themselves
as, or even mention, PSS, but all of them can be considered as PSS. This
paper is informed by the thinking underlying PSS, including the idea
that the resulting tools are more effective if they are modular and can
inter-link with other tools and processes in the planning process: PSS
can be conceived as a ``toolbox with separate instruments that can work
and talk to each other effectively (as in the open systems concept) and
that will be selectively applied in varying configurations to support a
particular phase in the planning process'' \citep{geertman2002}. We
share this conception of PSS, emphasizing the benefits of a focus on a
particular mode (cycling) and a particular phase in the planning process
(strategic network development).

Some of the most relevant existing tools are summarised below and
presented in Table~\ref{tbl-tools}.

@@

\includegraphics{images/paste-8.png}
\includegraphics{images/paste-9.png}

@@

\\
\toprule
Trip purpose & Description & Primary source(s) & Confidence\\
\midrule
\cellcolor{gray!10}{Work (commute)} & \cellcolor{gray!10}{Commuting to / from workplaces} & \cellcolor{gray!10}{Census 2016 POWSCAR Data} & \cellcolor{gray!10}{High confidence - data both origins and destinations for trip purposes}\\
Primary Education & Primary school trips & Census 2016 POWSCAR Data, Schools database & High confidence - data both origins and destinations for trip purposes\\
\cellcolor{gray!10}{Secondary Education} & \cellcolor{gray!10}{Secondary school trips} & \cellcolor{gray!10}{Census 2016 POWSCAR Data, Schools database} & \cellcolor{gray!10}{High confidence - data both origins and destinations for trip purposes}\\
Tertiary Education & Tertiary education trips & Census 2016 POWSCAR Data - Geodirectory categories & High confidence - data both origins and destinations for trip purposes\\
\cellcolor{gray!10}{Social} & \cellcolor{gray!10}{NHTS classification (e.g. restaurants, cinemas, gyms etc.)} & \cellcolor{gray!10}{Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes} & \cellcolor{gray!10}{Medium Confidence}\\
\addlinespace
Shopping & NHTS classificationfrom supermarkets and shops & Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes & Medium Confidence\\
\cellcolor{gray!10}{Personal / other} & \cellcolor{gray!10}{Combination of two NHTS classifications, and includes trips to medical, personal services and others} & \cellcolor{gray!10}{Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes} & \cellcolor{gray!10}{Medium Confidence}\\
Tourism / recreational & Trips by non-resident visitors to / from visitor attractions & Geodirectory listings for accommodation (origins) and destinations (destinations) & Failte Ireland accommodation database, Failte Ireland attraction database\\
\bottomrule

@@

We computed three route types for each disaggregated (`jittered') OD
pair: `Fastest', `Balanced' and `Quietest'. As outlined on the
CycleStreets'
\href{https://www.cyclestreets.net/help/journey/howitworks/}{website},
the fastest routes minimize journey time, accounting for traffic lights
and surface type. The `Quietest' route type minimizes busy sections of
road, allowing high `diversion factors' from the fastest route on
quieter but less direct ways (often avoiding roads and interactions with
motor vehicles altogether where possible). The `Balanced' route type is
a compromize between the two, minimising journey time while avoiding the
busiest roads. Allowing users to switch between these three route types
enables them to consider the trade-offs between directness and `cycle
friendliness' when planning new infrastructure, as shown in
Figure~\ref{fig-route-types}. These different network maps are available
on the `Route types' page for each county (see
\href{https://cruse.bike/kildare/route-types}{cruse.bike/kildare/route-types}
for Kildare, for example). In addition to showing the estimated routes
under each scenario, the page also presents summary statistics on the
network:

@@

\begin{minipage}{0.50\linewidth}
\includegraphics[width=2.60417in,height=\textheight]{images/naas_quietest_godutch.png}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics[width=2.60417in,height=\textheight]{images/naas_fastest_godutch.png}\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}
\includegraphics[width=2.60417in,height=\textheight]{images/newbridge_quietest_godutch.png}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics[width=2.60417in,height=\textheight]{images/newbridge_fastest_godutch.png}\end{minipage}%

@@

The CRUSE web application is statically hosted, meaning it does not
require a server running software such as the R package `shiny' or
Python packages such as `streamlit' or `flask' in the background
\citep{wickham2021}. This reduces hosting costs and the maintenance
burden of the tool compared with tools such as the PCT, and makes the
map-based interface more responsive, using the recently developed
`MapLibre' JavaScript package and `PMTiles' ``cloud native'' vector tile
format \citep{gonçalves2023}. The default view in landing page is of a
map of Ireland with county level results for the \% trips that could be
made by cycling under the `Go Dutch' scenario, highlighting the intended
use case for strategic cycle network planning and level of ambition. The
key results, route network results, are available within an instant by
zooming in on the map illustrated in Figure~\ref{fig-landing}: beyond a
certain zoom level the network view appears. This differs from the user
interface in tools such as the PCT and BiclaR which force users to click
on a county before the key network results become visible: to get to the
network view in the PCT takes around 10 seconds and multiple clicks,
compared with simply zooming in on the landing page for CRUSE.

@@

\includegraphics{images/paste-10.png}

@@

\caption{\label{fig-landing}Illustration of the landing page of the
CRUSE Tool for Ireland.}

@@

@@

\includegraphics[width=3.31in,height=\textheight]{images/fig5.png}

@@

\includegraphics{images/fig5.png}

@@

To illustrate the results in urban areas, we took the top 4 cities in
Ireland by population: Dublin City, Cork, Limerick and Galway (with city
populations of 0.6, 0.2, 0.1 and 0.1 million respectively). In
Figure~\ref{fig-city-results} we present the cycle route networks within
a 3km radius circle centred on each of these cities.

@@

\caption{\label{fig-city-results}Fastest, balanced and quietest cycle
networks within 3km circular areas containing the four largest cities in
Ireland. The networks are coloured by cycle friendliness, with greener
segments representing more cycle friendly segments. Widths vary in
proportion to the potential level of cycling under the `Go Dutch'
scenario.}

@@

Aside from the widely varying sizes and route networks of each city,
with Dublin having by far the densest network, it is clear from the
visualisation of cycling friendliness that there are many gaps in the
networks. Dublin has had received most investment in cycling
infrastructure and this is apparent from the high proportion of the
route network that is green, even in the fastest route network
representing routes that prioritize speed and directness over comfort
and safety. Dublin also has the highest mode share of cycling of the
four cities, adding to the evidence base showing that investment in
cycling infrastructure is effective in increasing cycling uptake.

Although Dublin City has made progress, there are still many parts of
the fastest route network, and even some parts of the Balanced and
Quietest route networks, that are not cycle friendly and which have high
cycling potential. According to a recent report, 71\% of residents in
the Dublin Metropolitan Area support ``more cycle tracks along roads,
physically separated from traffic and pedestrians'' \citep{walking2021}.
The results for the Dublin area could help prioritise investment in
cycling infrastructure in the city.

@@

While the CRUSE Tool is not the first national and publicly available
tool for cycling planning, it has some key features that make it
relevant for other countries, regions and road authorities tasked with
making their transport systems safe and sustainable:

\begin{itemize}
\tightlist
\item
  The results are \emph{open access} meaning that any stakeholder in the
  planning system can access the evidence. This will help to democratize
  the transport planning process and make wider conversations about
  transport planning more evidence-based and less polarized
  \citep{lovelace2020}, something that is particularly relevant given
  the potentially polarizing nature of pro-cycling interventions
  \citep{wild2017}.
\item
  The results are fully reproducible (code to be released pending
  sign-off by TII's IT team), preventing `cloud lock in' to a
  potentially monopolistic consultancy, and encouraging input from the
  wider open source community \citep{lovelace2021, dhir2017}.
\item
  By covering a wide range of trip purposes --- not just travel to work
  \citep{lovelace2017, heinen2010} and travel to school
  \citep{goodman2019} as covered in previously published research on
  open access national cycle network planning tools --- the results
  capture a higher proportion of cycling potential including key rural
  trips which are often under-represented in models of active travel.
\end{itemize}

As the benefits of strategic planning for cycling become more apparent
\citep{scappini2022}, we expect the demand for tools such as CRUSE to
grow. However, the approach is not without limitations and does not meet
all requirements in Ireland or indeed any country where the methods are
applied.

@@

Another limitation of the approach is that the results are `static',
reducing its ability to support monitoring of growth in cycling,
upgrades of existing cycling infrastructure and dynamic (year-by-year)
exposure information to estimate crash rates. Exposure information is a
key part of the the European RISM Directive, for reporting collision
rates of vulnerable road users by 2024. These factors mean that the tool
can be seen as an open access `leverage point', providing key
information for and supporting ambitious plans in many aspects the
planning system, from network design to post-build monitoring
\citep{lovelace2020}.

@@

The CRUSE Tool and the underlying research and methods are not without
limitations, suggesting future areas of research, data collection needs,
and policy application. The route network level results have not been
validated to the extent we had planned at the outset of the project. We
compared route network level results with `ground truth' data from cycle
counter datasets across Dublin to test different network types and to
ensure that additional trip types added to work and educational trips
increased the quality of fit under the baseline scenario. However, the
size of the counter network was insufficient to provide an opportunity
for robust evaluation of model performance, suggesting a combined
program of new count data collection and analysis should be a priority
for future work, with findings feeding directly into work to improve the
outputs of the the CRUSE Tool.

The CRUSE Tool is already used in practice to support more ambitious and
data-driven planning for safe cycling routes in multiple counties across
Ireland. We hope that the underlying approach, and the publicly
available evidence provided in the CRUSE Tool itself, provide a basis
for future reproducible research, open source software development into
strategic cycle network planning tools in Ireland and other countries.
Active travel represents a win-win-win for physical activity,
environment, and local economic opportunities. In combination with
broader sustainable mobility measures and policies to reduce motor
traffic speeds and volumes, tools such as CRUSE can support the fast and
fair decarbonisation of transport systems worldwide.

>>>>

\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={Cycle Route Uptake and Scenario Estimation (CRUSE): an approach for developing strategic cycle network planning tools},
  pdfkeywords={Cycling, Open-source, Road Safety, Active
Travel, Transport Planning, Collaborative Planning},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

@@

\begin{frontmatter}
\title{Cycle Route Uptake and Scenario Estimation (CRUSE): an approach
for developing strategic cycle network planning tools}

@@

Previous studies have applied the concept of PSS to specific modes,
including walking \citep{bencekri2024}, public transport
\citep{barmentlo2012} and cycling \citep{bencekri2023}. While such prior
work provides insight into the potential for approaches to transport
planning that are both data-driven and participatory, the focus of this
paper is on tools that focus attention on the \emph{geographic
distribution} of cycling potential and which answer the question ``where
to build''. Not all papers reviewed in this section classify themselves
as, or even mention, PSS, but all of them can be considered as PSS. This
paper is informed by the thinking underlying PSS, including the idea
that the resulting tools are more effective if they are modular and can
inter-link with other tools and processes in the planning process: PSS
can be conceived as a ``toolbox with separate instruments that can work
and talk to each other effectively (as in the open systems concept) and
that will be selectively applied in varying configurations to support a
particular phase in the planning process'' \citep{geertman2002}. We
share this conception of PSS, emphasizing the benefits of a focus on a
particular mode (cycling) and a particular phase in the planning process
(strategic network development). A selection of existing tools are
summarised below and presented in Table~\ref{tbl-tools}.

\newpage

@@

\includegraphics{paste-8.png} \includegraphics{paste-9.png}

@@

\toprule
Trip purpose & Description & Primary source(s) & Confidence\\
\midrule
\cellcolor{gray!10}{Work (commute)} & \cellcolor{gray!10}{Commuting to / from workplaces} & \cellcolor{gray!10}{Census 2016 POWSCAR Data} & \cellcolor{gray!10}{High confidence - data both origins and destinations for trip purposes}\\
Primary Education & Primary school trips & Census 2016 POWSCAR Data, Schools database & High confidence - data both origins and destinations for trip purposes\\
\cellcolor{gray!10}{Secondary Education} & \cellcolor{gray!10}{Secondary school trips} & \cellcolor{gray!10}{Census 2016 POWSCAR Data, Schools database} & \cellcolor{gray!10}{High confidence - data both origins and destinations for trip purposes}\\
Tertiary Education & Tertiary education trips & Census 2016 POWSCAR Data - Geodirectory categories & High confidence - data both origins and destinations for trip purposes\\
\cellcolor{gray!10}{Social} & \cellcolor{gray!10}{NHTS classification (e.g. restaurants, cinemas, gyms etc.)} & \cellcolor{gray!10}{Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes} & \cellcolor{gray!10}{Medium confidence}\\
\addlinespace
Shopping & NHTS classificationfrom supermarkets and shops & Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes & Medium confidence\\
\cellcolor{gray!10}{Personal / other} & \cellcolor{gray!10}{Combination of two NHTS classifications, and includes trips to medical, personal services and others} & \cellcolor{gray!10}{Trip rates from NHTS, Geodirectory businesses classified according to relevant NACE codes} & \cellcolor{gray!10}{Medium confidence}\\
Tourism / recreational & Trips by non-resident visitors to / from visitor attractions & Geodirectory listings for accommodation (origins) and destinations (destinations), Failte Ireland accommodation database, Failte Ireland attraction database & Low confidence - lack of data regarding tourist trip rates\\
\bottomrule

@@

We computed three route types for each disaggregated (`jittered') OD
pair: `Fastest', `Balanced' and `Quietest', based on the observation
that different cyclists have different preferences for route types and
the fastest or shortest path may not be the most heavily used
\citep{desjardins2022}. As outlined on the CycleStreets'
\href{https://www.cyclestreets.net/help/journey/howitworks/}{website},
the fastest routes minimize journey time, accounting for traffic lights
and surface type. The `Quietest' route type minimizes busy sections of
road, allowing high `diversion factors' from the fastest route on
quieter but less direct ways (often avoiding roads and interactions with
motor vehicles altogether where possible). The `Balanced' route type is
a compromise between the two, minimizing journey time while avoiding the
busiest roads. Allowing users to switch between these three route types
enables them to consider the trade-offs between directness and `cycle
friendliness' when planning new infrastructure, as shown in
Figure~\ref{fig-route-types}. These different network maps are available
on the `Route types' page for each county (see
\href{https://cruse.bike/kildare/route-types}{cruse.bike/kildare/route-types}
for Kildare, for example). In addition to showing the estimated routes
under each scenario, the page also presents summary statistics on the
network:

@@

\begin{minipage}{0.50\linewidth}
\includegraphics[width=2.60417in,height=\textheight]{naas_quietest_godutch.png}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics[width=2.60417in,height=\textheight]{naas_fastest_godutch.png}\end{minipage}%
\newline
\begin{minipage}{0.50\linewidth}
\includegraphics[width=2.60417in,height=\textheight]{newbridge_quietest_godutch.png}\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
\includegraphics[width=2.60417in,height=\textheight]{newbridge_fastest_godutch.png}\end{minipage}%

@@

The CRUSE web application is statically hosted, meaning it does not
require a server running software such as the R package `shiny' or
Python packages such as `streamlit' or `flask' in the background
\citep{wickham2021}. This reduces hosting costs and the maintenance
burden of the tool compared with tools such as the PCT, and makes the
map-based interface more responsive, using the recently developed
`MapLibre' JavaScript package and `PMTiles' ``cloud native'' vector tile
format \citep{gonçalves2023}. These open source technologies were used
to generate default view in the landing page: a map of Ireland with
county level results for the \% trips that could be made by cycling
under the `Go Dutch' scenario, highlighting the intended use case for
strategic cycle network planning and level of ambition, as illustrated
in Figure~\ref{fig-landing}.

@@

\includegraphics{paste-10.png}

\includegraphics{paste-11.png}

@@

\caption{\label{fig-landing}Illustration of the landing page of the
CRUSE Tool for Ireland, showing the default `zoomed out' view of the
national map, with county level results showing the proportion of trips
cycled under the `Go Dutch' scenario (top). The default `zoomed out'
view enables users to click on a county for more detailed results. The
`zoomed in' view shows the national network view for the `Go Dutch'
scenario for the Limerick area (bottom).}

@@

The key results, route network results, are available within an instant
by zooming in on the map illustrated in Figure~\ref{fig-landing}: beyond
a certain zoom level the network view appears. This differs from the
user interface in tools such as the PCT and BiclaR which force users to
click on a county before the key network results become visible: to get
to the network view in the PCT takes around 10 seconds and multiple
clicks, compared with simply zooming in on the landing page for CRUSE.

@@

@@

\includegraphics{fig-user-stories-1.pdf}

@@

To illustrate the results in urban areas, we explored route networks in
the three largest cities in Ireland: Dublin, Cork, and Limerick.
Figure~\ref{fig-city-results} shows the `fastest' and `quietest' cycle
networks within a 6km wide square centred on each of these cities.

@@

\caption{\label{fig-city-results}Fastest (left) and quietest (right)
cycle networks in 6 km squares centered on central Dublin (top panels)
Cork (middle) and Limerick (bottom). The networks are coloured by cycle
friendliness, with greener segments representing more cycle friendly
segments. Widths vary in proportion to the potential level of cycling
under the `Go Dutch' scenario.}

@@

Aside from the varying sizes and route network shapes associated with
each city, it is clear from the visualisation of cycling friendliness
that none of the cities can be considered to have a `complete' cycle
network. Of the three, Dublin has clearly had most investment cycle
infrastructure, as shown by the relatively high proportion of the route
network that is green in both network types.

Figure~\ref{fig-city-results} highlights the value of generating
different network types: looking only at the fastest network it would be
hard to differentiate between Cork and Limerick in terms of cycle
network quality. However, Limerick clearly has a higher number of quiet
routes that can be cycled on for people willing to take a longer route
to avoid busy roads: its quiet network (bottom right in
Figure~\ref{fig-city-results}) contains more green segments than the
quietest network for Cork (middle right in
Figure~\ref{fig-city-results}). The lack of continuous sections of quiet
routes in Cork, even in the quietest network, means that people who are
less confident cycling \emph{cannot} avoid mixing with motor traffic for
many common trips. In an ideal network, conversely, even the fastest
route network would be predominantly cycle friendly, meaning that the
most direct and fast routes are also quiet, with low levels of traffic
stress.

There are still many parts of the fastest route network, and even some
parts of the quietest route networks, that are not cycle friendly and
which have high cycling potential, even in Dublin. According to a recent
report, 71\% of residents in the Dublin Metropolitan Area support ``more
cycle tracks along roads, physically separated from traffic and
pedestrians'' \citep{walking2021}. Assuming that these findings apply in
other cities, the results can help prioritise where such infrastructure
should go: the results presented in Figure~\ref{fig-city-results} should
bring attention to where there are wide red lines in fastest and
quietest networks, with a reasonable strategy being to prioritise a
continuous quiet network first and eventually to `cycle proof' the
fastest network also. However, a feature of the approach is that it is
not prescriptive and it does not tell planners what to build where; as
highlighted below practitioners can use the results in a variety of
ways.

@@

While the CRUSE approach presented in this paper is not the first
national and publicly available tool for cycling planning, it has some
key features that make it relevant for other countries, regions and road
authorities tasked with making their transport systems safe and
sustainable:

\begin{itemize}
\tightlist
\item
  Compared with the Propensity to Cycle Tool (PCT), which provides
  either travel to work \citep{lovelace2017} or to school cycling
  networks \citep{goodman2019}, the approach presented here captures a
  higher proportion of cycling potential including key rural trips which
  are often under-represented in models of active travel.
\item
  The results are \emph{open access} meaning that any stakeholder in the
  planning system can access the evidence. This will help to democratize
  the transport planning process and make wider conversations about
  transport planning more evidence-based and less polarized
  \citep{lovelace2020}, something that is particularly relevant given
  the potentially polarizing nature of pro-cycling interventions
  \citep{wild2017}.
\item
  The results are fully reproducible (code to be released pending
  sign-off by TII's IT team), preventing `cloud lock in' to a
  potentially monopolistic consultancy, and encouraging input from the
  wider open source community \citep{lovelace2021, dhir2017}.
\item
  The tool has a user interface that allows people to see the key
  results quickly, without having to click on regional result pages, as
  is the case with the BiclaR and PCT projects.
\end{itemize}

As the benefits of strategic planning for cycling become more apparent
\citep{scappini2022}, we expect the demand for the approach outlined in
this paper, and resulting tools, to grow. However, the approach is not
without limitations and does not meet all requirements in Ireland or
indeed any country where the methods are applied.

@@

Another limitation of the approach is that the results are `static',
reducing its ability to support monitoring of growth in cycling,
upgrades of existing cycling infrastructure and dynamic (year-by-year)
exposure information to estimate crash rates. Exposure information is a
key part of the the European RISM Directive, for reporting collision
rates of vulnerable road users by 2024. Regular updates to the model to
generate yearly baseline cycle flow estimates could tackle this
limitation, although would take substantial resources.

@@

As outlined in Section~\ref{sec-qualitative}, the tool is already used
in practice to support more ambitious and data-driven planning for safe
cycling routes in multiple counties across Ireland. We hope that the
underlying approach provides a basis for future research and
development. In combination with broader sustainable mobility measures
and policies to reduce motor traffic speeds and volumes, evidence
generated by the approach outlined in this paper can support the fast
and fair decarbonisation of transport systems worldwide.
